\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{appendix}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{fontspec}
\usepackage[bottom]{footmisc}
\usepackage[margin=0.9in,footskip=0.25in]{geometry}
\usepackage{graphicx}
\usepackage{lscape}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{subcaption}
\usepackage{subfloat}
\bibliographystyle{abbrvnat}\bibpunct{(}{)}{;}{a}{,}{,}

%%%%
%%%%  NOTE: THIS MUST BE COMPILED WITH xelatex!
%%%%
\setmainfont{Times New Roman}
\setlength{\parskip}{6pt}


\title{The Long-Term and Intergenerational Effects of Neonatal Health Interventions\thanks{We are grateful to X, Y and Z for useful comments, and to seminar audiences at A, B and C. Clarke acknowledges financial support from ANID Chile (FONDECYT Regular 1200634).  OTHER.  }}
\author{Damian Clarke\thanks{Department of Economics, University of Chile \& IZA.  Contact:}
  \and Nicol\'as Lillo\thanks{Department of Economics, University of Chile.  Contact:}
  \and Kathya Tapia Schythe\thanks{Department of Economics, University of California, Davis.  Contact:}
}
\date{\today}

\begin{document}
\begin{spacing}{1.5}
  \maketitle

  \begin{abstract}
    Targeted treatments of new-borns with delicate health stocks have been shown to have considerable returns in terms of survival and later life outcomes.  We seek to determine to what degree such treatments are reflected in later life health outcomes of treated individuals, and to what degree these are passed on to early life health outcomes of the \emph{subsequent} generation.  We follow three generations of linked microdata, and use a regression discontinuity design to study the impacts of targeted neonatal health policies based on birth weight assignment rules.  We estimate that...
  \end{abstract}

  \noindent JEL Codes: I11; I18; J13; H51; O15. \\
  Keywords: Early life interventions; intergenerational mobility; health care provision. \\
  %\end{spacing}

  \clearpage

  \section{Introduction}

  \clearpage
  \section{Background and Context}
  \citet{Almondetal2010,Bharadwajetal2013}
  
  
  \clearpage
  \section{Data}

  \clearpage
  \section{Methods}

  \clearpage
  \section{Results}

  \clearpage
  \section{Discussion}

  \clearpage
  \bibliography{refs}
  
  \clearpage
  \begin{appendices}
  \setcounter{page}{1}
  \renewcommand{\thepage}{A\arabic{page}}
  \setcounter{table}{0}
  \renewcommand{\thetable}{A\arabic{table}}
  \setcounter{figure}{0}
  \renewcommand{\thefigure}{A\arabic{figure}}



  \section{Data Consistency}

  In progress...
  \begin{table}[htpb!]
    \centering
    \caption{Data Consistency Checks of Matched Microdata Bases}
    \begin{tabular}{lccc} \toprule
      Births & Hospitalization & Deaths \\ \midrule
    \end{tabular}
  \end{table}

  \clearpage
  \section{Appendix Figures and Tables}
    
  \end{appendices}
\end{spacing}
\end{document}
